---
title: "Create anchor genes expr file"
author: "Frederick Boehm"
date: "11/29/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Since I don't have the expression data for the four anchor genes in a single file, I'll make such a file now.

I know that the filenames for run 3102 contain the names of three anchor genes (four minus one, where the one is Asah2, which is in run 3101). 

```{r}
library(tidyverse)
```



```{r}
scans <- list()
fns <- dir("../results/pvl-run3102/", pattern = ".txt")
for (i in 1:length(fns)){
  scans[[i]] <- as_tibble(read.table(file.path("../results/pvl-run3102", fns[i])))
}
# lrt <- purrr::map_dbl(.x = scans, .f = calc_lrt_tib)
```

Now, we parse the filenames to get the annotation information.

```{r}
gene1 <- str_split(fns, pattern = "_") %>%
  purrr::map_chr(.f = function(x)x[3])
gene2 <- str_split(fns, pattern = "_") %>%
  purrr::map_chr(.f = function(x)x[4]) %>% 
  str_split(pattern = ".txt") %>%
  purrr::map_chr(.f = function(x)x[1])
```

```{r}
table(gene1)
(table(gene2) %>% names() -> anchors)
```
So, we see that the 3 anchor genes are:

ENSMUSG00000024766
ENSMUSG00000087303
ENSMUSG00000089952

Now, load the Attie data set.

```{r}
readRDS("../data-to-condor/chr19_expr_10mb.rds") -> expr
anchors %in% colnames(expr)
saveRDS(expr[ , colnames(expr) %in% anchors], file = "../data-to-condor/expr_anchors.rds")
```



