---
title: "Examining allele effects for chromosome 19 traits"
author: "Frederick Boehm"
date: "10/30/2018"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

We first load the Rdata file from Data Dryad.

```{r}
load("../data/Attie_DO378_eQTL_viewer_v1.Rdata")
```

```{r}
foo <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == 19, lod > 10)

(dat <- dataset.islet.rnaseq$annots %>% 
  filter(chr == 19) %>%
  right_join(foo, by = c("gene_id" = "annot.id")) %>%
  filter(chrom == 19, chr == 19) %>%
  arrange(desc(lod))
 )
```

We have `r nrow(dat)` local traits (with lods greater than 10) on chromosome 19.

Let's create a histogram of the QTL peak positions.

```{r}
hist(dat$pos)
```


*Asah2* has a LOD above 100 and is near the center of the chromosome. The four genes with greater LODs are not near the middle of the chromosome. It also looks like *Asah2* has some interesting biology, per its wikipedia page: https://en.wikipedia.org/wiki/ASAH2





```{r}
dat %>%
  filter(symbol == "Asah2")
asah2_id <- dat %>%
  filter(symbol == "Asah2") %>%
  select(gene_id) %>%
  unlist()
```

We can then isolate the *Asah2* expression values.

```{r}
asah2_expr <- dataset.islet.rnaseq$expr[ , colnames(dataset.islet.rnaseq$expr) == asah2_id, drop = FALSE]
```



Now, we save the 378 mice by 346 traits - including Asah2 - expression matrix for later use with Condor.

```{r}
trait_ids <- dat %>% 
  select(gene_id) %>%
  unlist()
```

```{r}
expr_chr19 <- dataset.islet.rnaseq$expr[ , 
                           colnames(dataset.islet.rnaseq$expr) %in% trait_ids, 
                           drop = FALSE]
```

Now, let's save the expression traits for only those traits with peak positions within 10 Mb of the peak position for *Asah2*.

```{r}
asah2_pos <- dat %>%
  filter(symbol == "Asah2") %>%
  select(pos) %>%
  unlist()
trait_ids_10mb <- dat %>% 
  filter(pos < asah2_pos + 10, pos > asah2_pos - 10) %>%
  select(gene_id) %>%
  unlist()

```

```{r}
expr_chr19_10mb <- dataset.islet.rnaseq$expr[ , 
                           colnames(dataset.islet.rnaseq$expr) %in% trait_ids_10mb, 
                           drop = FALSE]
```



## Examine the map object to see how many markers are spanned by the traits in chr19_expr_10mb.rds

```{r}
m19 <- map$`19`
m19_tib <- tibble(marker_id = names(m19), position = m19)
which(m19_tib$position > 22)[1]
which(m19_tib$position > 42)[1]
```

## Calculate allele effects for Asah2

```{r}
library(qtl2)
```

```{r}
s1c_asah2 <- scan1coef(genoprobs = genoprobs[, 19], pheno = asah2_expr, kinship = K$`19`, addcovar = dataset.islet.rnaseq$covar[ , -5], reml = TRUE)
```

```{r}
plot_coefCC(x = s1c_asah2, map = map)
```

## Calculate allele effects for many traits near Asah2

```{r}
traits_of_interest <- c("ENSMUSG00000038658", 
                        "ENSMUSG00000024766",
                        "ENSMUSG00000087303", 
                        "ENSMUSG00000087112", 
                        "ENSMUSG00000079344")
expr_for_ae <- expr_chr19[ , colnames(expr_chr19) %in% traits_of_interest]

s1c_out <- list()

for (i in 1:length(traits_of_interest)){
  s1c_out[[i]] <- scan1coef(genoprobs = genoprobs[, 19], pheno = expr_for_ae[ , i], kinship = K$`19`, addcovar = dataset.islet.rnaseq$covar[ , -5], reml = TRUE)

}
```

```{r}
for (i in 1:length(s1c_out)){
  plot_coefCC(x = s1c_out[[i]], map = map)
}
```






